### 2020-04-08 draft.tex
another thing
MEs

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'', but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}.

@@

\begin{acknowledgements}
Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600.
Spivak acknowledges support from AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
\end{acknowledgements}

@@

The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
which the following square is a pullback
\[
  \begin{tikzcd}[column sep=large]
0 \arrow[r] \arrow[d] \arrow[dr, phantom,
"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
\term{ZC}(\pi) \arrow[r, hookrightarrow]                                       & B
\end{tikzcd}
\]
\end{proof}
We prove a few quick facts we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
  of connected components of its indexing category. Since we assumed the
  indexing category was connected, this contains a single element.
\end{proof}

@@

As a corollary, any $\pi : \downarrow \to \Set$ equals the composite
$$\downarrow \xto{\sigma} (\downarrow)\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
(\Set^{\downarrow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
One checks directly.
\end{proof}

@@

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$ --- see Corollary 9.5.3 of \cite{RV:Elements}. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).

>>>>

\section{Introduction}
A polynomial functor $P : \Set \to \Set$ is a sum of representables
\begin{equation}\label{eqn.poly}
P(X) := \sum_{b \in B} X^{E_b}
\end{equation}
where the family of sets $E_b$ depends on $b\in B$. This data is known
in the computer science literature as a ``container'' \cite{Abbott}, but since such an indexed
family of sets can be represented by as a function
\[
  \begin{tikzcd}
    E \arrow[d, "\pi"] \\
    B
  \end{tikzcd}
\]
we will refer to it as a \emph{bundle}.

@@

\begin{acknowledgements}
Joyal, Kock(!), AFOSR. David Jaz Myers was supported by the National Science Foundation grant DMS-1652600 and Spivak was supported by AFOSR grants FA9550-19-1-0113 and FA9550-17-1-0058.
\end{acknowledgements}

@@

The existence of the final adjoint can be deduced from the fact that $!^{(-)}$ preserves all
limits. It sends a bundle $\pi : E \to B$ to the largest subset $\term{ZC}(B)$ of $B$ for
which the following square is a pullback
\[
  \begin{tikzcd}[column sep=large]
0 \arrow[r] \arrow[d] \arrow[dr, phantom,
"\ulcorner" very near start] & E \arrow[d, "\pi"] \\
\term{ZC}(\pi) \arrow[r, hookrightarrow]                                       & B
\end{tikzcd}
\qedhere
\]
\end{proof}
We prove a few quick facts we will use later.
\begin{lem}\label{lem:bang.preserves.connected.colimits}
  The functor $!_{(-)}\colon\Set\to\Set^{\down}$ from \eqref{eqn.bangbang} preserves connected colimits.
\end{lem}
\begin{proof}
  To see that $!_{(-)}$ preserves connected colimits, recall that colimits in $\Set^{\down}$ are calculated pointwise. It remains to show, then, that the map of bundles
  \[
    \begin{tikzcd}
    \colim S_i \arrow[r, equals] \arrow[d] & \colim S_i \arrow[d] \\
    \colim \ast \arrow[r] & \ast 
    \end{tikzcd}
  \]
  is an isomorphism in $\Set^{\down}$, for which it suffices to show that
  $\colim \ast$ is terminal. But the colimit of a diagram of terminal objects is the set
  of connected components of its indexing category. Since we assumed the
  indexing category was connected, this contains a single element.
\end{proof}

@@

As a corollary, any $\pi : \downarrow \to \Set$ is naturally isomorphic to the composite
$$\downarrow \xto{\sigma} (\downarrow)\op \xto{!_0\op} \Set\op \xto{!_{(-)}\op}
(\Set^{\downarrow})\op \xto{\Set^{\downarrow}(-, \pi)} \Set$$
by the Yoneda lemma.
\end{lem}
\begin{proof}
One checks directly.
\end{proof}

@@

First, we note that 
$$S \mapsto \lim(\Hom_{\Set\op}(S, !_0\op \circ \sigma) \to \down \xto{\pi} \Set)$$
is the right Kan extension formula for $\ext_{\pi} \equiv
\term{ran}_{!_0} \pi$. Now,
$\Hom_{\Set\op}(S, !_0\op \circ \sigma) \simeq \Hom_{\Set}(!_0 \circ \sigma\op,
S)\op$ over $\down$. Furthermore, we have the following equivalence:
\[
% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAB12AJCAWwH1gnLnQC+ACgCE-YgAJOAYywAnBfPbYA5rzqcIaUrIDKASj1oQo0uky58hFGQCMVWoxZthfQcLFSZhqbmltYgGNh4BERO5K70zKyIHOxQEADuhFY2EfbRpC7U8R5JnKkZwaKuMFCa8ESgAGbKfEhkIDgQSDEgDHQARjAMAAq2kQ4gyliaABY4IIXuicnYvCGNzauIbR1IAExZIE0tiLvUO4gAzAsJnhpTOmuHG11nnZeVokA
\begin{tikzcd}
{\Hom_{\Set}(!_0 \circ \sigma\op, S)\op} \arrow[d, "\sim"'] \arrow[r] & \down \arrow[d, "\sigma"] \\
{\Hom_{\Set}(!_0, S)\op} \arrow[r]                                    & \down\op                 
\end{tikzcd}
\]
and therefore we may equivalently calculate this limit as 
$$\lim(\Hom_{\Set}(!_0, S)\op \to \down\op \xto{\sigma\op} \down \xto{\pi} \Set).$$
This gives us the equivalence between (1) and (5).
